---
name: Tomás Capretto
#surname: Capretto
position: "Doctorate Candidate"
address: "IMASL/CONICET"
www: tcapretto.netlify.com
github: tomicapretto
email: "tomicapretto@gmail.com"
aboutme: "Statistician interested in R, Python, R Shiny and anything that improves how we do data analysis"
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 2f3640
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Education

```{r education}
tribble(
  ~ degree, ~ dates, ~ uni, ~ where, ~ details,
  "Doctorate in Statistics", "2019-2024 (expected)", "Universidad Nacional de Rosario", 
  "Rosario, Argentina", 
  paste(
    "I work under the supervision of PhD. Osvaldo Martin on Bayesian statistics",
    "and exploratory data analysis."
  ),

  "Doctorate in Statistics", "2019-2024 (expected)", "Universidad Nacional de Rosario", 
  "Rosario, Argentina", 
  paste(
    "Studied density estimators and implemented a new alternative for the Python",
    "package ArviZ.This implementation was then translated to R and included in bayesplot package."
  ),
  
  "Doctorate in Statistics", "2019-2024 (expected)", "Universidad Nacional de Rosario", 
  "Rosario, Argentina", 
  paste(
    "Currently focused on Bambi, a Python library that makes Bayesian model building easier."
  ),
  
  "Bachelor in Statistics", "2014-2019", "Universidad Nacional de Rosario", 
  "Rosario, Argentina", 
  paste(
  "The career gave me a solid background in foundations of statistics",
  "as well as the ability to interpret results in an analytical manner."
  ) 
) %>% 
  detailed_entries(degree, dates, uni, where, details) # Enables Latex code.
```

# Research experience

```{r research-experience}

tribble(
  ~ role, ~ date, ~ institution, ~ where, ~ details,
  
  "Research assistant", "Apr 2018 - Mar 2019", "Universidad Nacional de Rosario", "Rosario, Argentina", "\\textbf{Project:} Statistical methods in official statistics.", 
  "Research assistant", "Apr 2018 - Mar 2019", "Universidad Nacional de Rosario", "Rosario, Argentina", "Developed my undergraduate thesis \\textit{Estimation in complex survey samples in presence of nonresponse}.",
  
  "Research assistant", "Apr 2016 - Mar 2017", "Universidad Nacional de Rosario", "Rosario, Argentina", "\\textbf{Project:} Sampling designs based on models for populations with spatial variability.", 
  "Research assistant", "Apr 2016 - Mar 2017", "Universidad Nacional de Rosario", "Rosario, Argentina", "As a complement of a course in sampling techniques, I dedicated most of the time to the study of new sampling methods that incorporate spatial variability." 
) %>%
  detailed_entries(role, date, institution, where, details, .protect = FALSE) # Enables Latex code.
```


# Work experience

```{r work-experience}

tribble(
  ~ role, ~ date, ~ company, ~ where, ~ details,
  
  "Consultant", "Nov 2018 - Jan 2019", "AlixPartners", "Buenos Aires, Argentina", "Data manipulation and analysis using R, Python, SQL and Tableau.", 
  "Consultant", "Nov 2018 - Jan 2019", "AlixPartners", "Buenos Aires, Argentina", "Time series forecasting.",
  "Consultant", "Nov 2018 - Jan 2019", "AlixPartners", "Buenos Aires, Argentina", "Task automation.", 
  
  "Statistical assistant", "May 2018 - Oct 2018", "Instituto Nacional de Estadística y Censos", "Buenos Aires, Argentina", "I worked on the study of non-response, its classification and treatment.", 
  "Statistical assistant", "May 2018 - Oct 2018", "Instituto Nacional de Estadística y Censos", "Buenos Aires, Argentina", "Contributed to methodological manuals and internal reports.", 
  "Statistical assistant", "May 2018 - Oct 2018", "Instituto Nacional de Estadística y Censos", "Buenos Aires, Argentina", "Evaluation of methods to impute missing data.", 
  
  "Statistical assistant", "Jul 2016 - Sep 2016", "Universidad Nacional de Rosario", "Rosario, Argentina", "Survey sampling study to study characteristics of members from a professional college in Santa Fe province.",
  "Statistical assistant", "Jul 2016 - Sep 2016", "Universidad Nacional de Rosario", "Rosario, Argentina", "Participated in the strategy to collect the data.",
  "Statistical assistant", "Jul 2016 - Sep 2016", "Universidad Nacional de Rosario", "Rosario, Argentina", "Worked on the consistency of the data bases and the generation of internal reports.",
  "Statistical assistant", "Jul 2016 - Sep 2016", "Universidad Nacional de Rosario", "Rosario, Argentina", "Worked on telephone surveys and cases follow-up.",
  
) %>%
  detailed_entries(role, date, company, where, details, .protect = FALSE) # Enables Latex code.
```


\pagebreak

# Training experience

```{r teaching-experience}

tribble(
  ~ role, ~ date, ~ company, ~ where, ~ details,
  
  "Online tutor", "Aug 2018 - May 2019", "Chegg Tutors", "Remote", "Tutored Statistics, R and SAS Programming, and related topics in English.",
  "Online tutor", "Aug 2018 - May 2019", "Chegg Tutors", "Remote", "I worekd with both undergraduate and graduate students from a very wide range of disciplines.",

  "Online tutor", "Nov 2015 - Nov 2018", "Latinhire", "Remote", "Tutored Statistics both in English and Spanish.",
  "Online tutor", "Nov 2015 - Nov 2018", "Latinhire", "Remote", "Worked with both high-school and undergraduate students.",

) %>%
  detailed_entries(role, date, company, where, details, .protect = FALSE) # Enables Latex code.

```

# Scholarships, awards and distinctions

```{r awards}

tribble(
  ~ what, ~ date, ~ institution, ~ place, ~ details,
  
  "PhD scholarship in strategic topics", "2019 - 2024", "CONICET", "San Luis, Argentina", "\\textbf{Topic:} Exploratory analysis of Bayesian methods.",
  "PhD scholarship in strategic topics", "2019 - 2024", "CONICET", "San Luis, Argentina", "Full-time position dedicated to study and research.",
  
  "1st Prize in the XIII Young Biometrists Contest", "Oct 2017", "Grupo Argentino de Biometría", "Rosario, Argentina", "I worked with David Presutti, Agronomic Engineering student.", 
  "1st Prize in the XIII Young Biometrists Contest", "Oct 2017", "Grupo Argentino de Biometría", "Rosario, Argentina", "We used generalized mixed linear models to solve the proposed problem.", 
  
  "Fulbright scholar", "Jan 2017 - Feb 2017", "Comisión Fulbright Argentina", "Austin, United States", "I made a stay in the  University of Texas at Austin thanks to the scholarship Friends of Fulbright 2017.", 
  "Fulbright scholar", "Jan 2017 - Feb 2017", "Comisión Fulbright Argentina", "Austin, United States", "The activities involved english training, cultural exchange, volunteering and I also attended classes in Statistics.", 
  
) %>% 
  detailed_entries(what, date, institution, place, details, .protect = FALSE)
```

# Side projects

Out of curiosity or fun, I also dedicate part of my time to projects not directly 
related to my doctorate.

* [`latex2r`](https://github.com/tomicapretto/latex2r):
An R package to translate math formulas written in LaTeX to R code.
* [`shinymath`](https://github.com/tomicapretto/shinymath): Math inputs in R Shiny apps.
This package gives a new input that is based on Mathquill and returns R code.
* [`formulae`](https://github.com/tomicapretto/formulae): A WIP library that
enables using the popular R formulas in Python. While there is [`patsy`](https://github.com/pydata/patsy)
out there, this implementation also handles group specific effects
(a.k.a. random effects), among other features.
