---
name: Tomás
surname: Capretto
position: "PhD Candidate"
address: "IMASL/CONICET"
www: tcapretto.netlify.com
email: "tomicapretto@gmail.com"
github: tomicapretto
aboutme: Statistical learning, Statistical programming, Survey sampling
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::moderncv:
    theme: classic
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# About me

* Statistician interested in teaching, research and consulting.
* R \textbf{and} Python better than R \textbf{or} Python:  
R is my main programming tool and I enjoy it a lot. Though, I am investing much time in Python because I want to complement both.
* \textbf{My thoughts in a nutshell:} Big Data does not mean all data. More questions. Better ideas.

# Education

```{r education}

tribble(
  ~ what, ~ when, ~ with, ~ where, ~ why,
  
  "PhD in Statistics", "2019-2024 (expected)", "Universidad Nacional de Rosario", "Rosario, Argentina", "I am working under the supervision of PhD. Osvaldo Martín on Bayesian Statistics. At the time, we are currently working on Density estimators and its implementation in the Python package Arviz.",
  
  "Bachelor in Statistics", "2014-2019", "Universidad Nacional de Rosario", "Rosario, Argentina", "The career gave me a solid background in foundations of statistics and as well as the interpretation of results in an analytical manner."
) %>% 
  detailed_entries(what, when, with, where, why) # Enables Latex code.
```

# Research experience

```{r research-experience}

tribble(
  ~ what, ~ when, ~ with, ~ where, ~ why,
  
  "Research assistant", "Apr 2018 - Mar 2019", "Universidad Nacional de Rosario", "Rosario, Argentina", "\\textbf{Project:} Statistical methods in official statistics.", 
  "Research assistant", "Apr 2018 - Mar 2019", "Universidad Nacional de Rosario", "Rosario, Argentina", "Developed my undergraduate thesis \\textit{Estimation in complex survey samples in presence of nonresponse}.",
  
  "Research assistant", "Apr 2016 - Mar 2017", "Universidad Nacional de Rosario", "Rosario, Argentina", "\\textbf{Project:} Sampling designs based on models for populations with spatial variability.", 
  "Research assistant", "Apr 2016 - Mar 2017", "Universidad Nacional de Rosario", "Rosario, Argentina", "As a complement of a course in sampling techniques, I dedicated most of the time to the study of new sampling methods that incorporate spatial variability." 
) %>%
  detailed_entries(what, when, with, where, why, .protect = FALSE) # Enables Latex code.

```

# Teaching experience

```{r teaching-experience}

tribble(
  ~ what, ~ when, ~ with, ~ where, ~ why,
  
  "Online tutor", "Aug 2018 - May 2019", "Chegg Tutors", "Remote", "Tutored Statistics, R and SAS Programming, and related topics in English.",
  "Online tutor", "Aug 2018 - May 2019", "Chegg Tutors", "Remote", "I worekd with both undergraduate and graduate students from a very wide range of disciplines.",

  "Online tutor", "Nov 2015 - Nov 2018", "Latinhire", "Remote", "Tutored Statistics both in English and Spanish.",
  "Online tutor", "Nov 2015 - Nov 2018", "Latinhire", "Remote", "Worked with both high-school and undergraduate students.",

) %>%
  detailed_entries(what, when, with, where, why, .protect = FALSE) # Enables Latex code.

```

\pagebreak

# Work experience

```{r job-experience}

tribble(
  ~ what, ~ when, ~ with, ~ where, ~ why,
  
  "Consultant", "Nov 2018 - Jan 2019", "AlixPartners", "Buenos Aires, Argentina", "Data manipulation and analysis using R, Python, SQL and Tableau.", 
  "Consultant", "Nov 2018 - Jan 2019", "AlixPartners", "Buenos Aires, Argentina", "Time series forecasting.",
  "Consultant", "Nov 2018 - Jan 2019", "AlixPartners", "Buenos Aires, Argentina", "Task automation.", 
  
  "Statistical assistant", "May 2018 - Oct 2018", "Instituto Nacional de Estadística y Censos", "Buenos Aires, Argentina", "I worked on the study of non-response, its classification and treatment.", 
  "Statistical assistant", "May 2018 - Oct 2018", "Instituto Nacional de Estadística y Censos", "Buenos Aires, Argentina", "Contributed to methodological manuals and internal reports.", 
  "Statistical assistant", "May 2018 - Oct 2018", "Instituto Nacional de Estadística y Censos", "Buenos Aires, Argentina", "Evaluation of methods to impute missing data.", 
  
  "Statistical assistant", "Jul 2016 - Sep 2016", "Universidad Nacional de Rosario", "Rosario, Argentina", "Survey sampling study to study characteristics of members from a professional college in Santa Fe province.",
  "Statistical assistant", "Jul 2016 - Sep 2016", "Universidad Nacional de Rosario", "Rosario, Argentina", "Participated in the strategy to collect the data.",
  "Statistical assistant", "Jul 2016 - Sep 2016", "Universidad Nacional de Rosario", "Rosario, Argentina", "Worked on the consistency of the data bases and the generation of internal reports.",
  "Statistical assistant", "Jul 2016 - Sep 2016", "Universidad Nacional de Rosario", "Rosario, Argentina", "Worked on telephone surveys and cases follow-up.",
  
) %>%
  detailed_entries(what, when, with, where, why, .protect = FALSE) # Enables Latex code.

```


# Scholarships, awards and distinctions

```{r awards}

tribble(
  ~ what, ~ when, ~ with, ~ where, ~ why,
  
  "PhD scholarship in strategic topics", "2019 - 2024", "CONICET", "San Luis, Argentina", "\\textbf{Topic:} Exploratory analysis of Bayesian methods.",
  "PhD scholarship in strategic topics", "2019 - 2024", "CONICET", "San Luis, Argentina", "Full-time position dedicated to study and research.",
  
  "1st Prize in the XIII Young Biometrists Contest", "Oct 2017", "Grupo Argentino de Biometría", "Rosario, Argentina", "I worked with David Presutti, Agronomic Engineering student.", 
  "1st Prize in the XIII Young Biometrists Contest", "Oct 2017", "Grupo Argentino de Biometría", "Rosario, Argentina", "We used generalized mixed linear models to solve the proposed problem.", 
  
  "Fulbright scholar", "Jan 2017 - Feb 2017", "Comisión Fulbright Argentina", "Austin, United States", "I made a stay in the  University of Texas at Austin thanks to the scholarship Friends of Fulbright 2017.", 
  "Fulbright scholar", "Jan 2017 - Feb 2017", "Comisión Fulbright Argentina", "Austin, United States", "The activities involved english training, cultural exchange, volunteering and I also attended classes in Statistics.", 
  
) %>% 
  detailed_entries(what, when, with, where, why, .protect = FALSE)
```